---
title: "Process_SolisensePigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisensePigmentsData.Rmd processes and combines BalticPhotoperiod_Imported_SolisenseDarkafterLight.Rds and BalticPhotoperiod_Imported_SolisenseLight.Rds from Data/ImportedData/ImportedSolisenseData folder. This .Rmd generates BalticPhotoperiod_Processed_SolisenseData.Rds (stored in Data/ProcessedData/ProcessedSolisenseData folder), plots stored in Output/Figures folder, and tables stored in Output/TablesRds folder.

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(scales)
library(Cairo) #for greek symbols
library(googledrive)
library(googlesheets4)
library(readxl)
library(multcompView)
library("patchwork") # merging plots
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
```

```{r set project variables}
Project <- "BalticCCA"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData", fsep = .Platform$file.sep)


FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

# List and read Imported_Solisense RDS

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```


# This RDS contained only data from corresponding growth light 
# Also, conteined mean sig - mean for replica measured on the same day

```{r read ProcessFile Sol}
SolisenseFile <- "../Data/ImportedData/ImportedSolisenseData/BalticCCA_Imported_SolisenseLight_LRC.Rds"  

SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits <- readRDS(SolisenseFile)  %>%
  ungroup()

SolFitsMeta <- SolFits %>% 
  select(-c(nm445,nm470,nm505,nm535,nm590,IR, nm445Corr,nm470Corr, nm505Corr,nm535Corr,nm590Corr,IRCorr,JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig)) |>
  rename(JVPSII_ETRqpOxbo_FoSigmax_m2psii = JVPSII_ETRqpOxbo_FoSig) |>
  rename(FilenameSolisense=Filename) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich",
         Strain=="BA77G"~"PC-rich")) 

#colnames(SolFitsMeta)
```



# Calibrated JVPSII

To get the Platt fits to work I plotted:
JVPSII_umole_eLs vs. ActPAR

so I had to convert JVPSII_eLs by dividing by 6.022E-17.
If you want to go back to JVPSII_eLs just multiple back up.

# Calibrate JVPSII to e L-1 s-1

```{r JVPSII calib}
JVPSII_eLs_ModelTerms <- read_rds(file.path("..","Data", "CleanedData", "JVPSIIO2Calib", "SySlBiolSteps_TC_JVPSII_eLs_ModelTerms.Rds"))

#smarter way to code this with 'which' in [] and map through Ex_WL
SolFitsMeta <- left_join(SolFitsMeta, JVPSII_eLs_ModelTerms, by = join_by(Ex_WL)) |>
  select(-c(Slope_P)) |>
  mutate(JVPSII_eLs = JVPSII_ETRqpOxbo_FoSigmax_m2psii/Slope) |>
  mutate(JVPSII_umol_eLs = JVPSII_eLs/6.022e17)

```



-------------------------------# Create df with phases of growth---------------------------------

```{r}
MultiCultiDataAll70ExpResup<-SolFitsMeta %>% 
  filter(E_days >= 14)  
MultiCultiDataAll70ExpResup$Phase<-"ExpResuply"

All70PCExp1<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days < 14)  
All70PCExp1$Phase<-"Exp"

All70PCExp2<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 8)  
All70PCExp2$Phase<-"Exp"

All70PCExp3<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp3$Phase<-"Exp"

All70PCExp4<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp4$Phase<-"Exp"

All70PCSt1<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 9 & E_days <=13)  
All70PCSt1$Phase<-"St"

All70PCSt2<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt2$Phase<-"St"

All70PCSt3<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt3$Phase<-"St"




All70PEExp1<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp1$Phase<-"Exp"

All70PEExp2<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp2$Phase<-"Exp"

All70PEExp3<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days < 14)  
All70PEExp3$Phase<-"Exp"

All70PEExp4<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp4$Phase<-"Exp"


All70PESt1<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt1$Phase<-"St"

All70PESt2<-SolFitsMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt2$Phase<-"St"

All70PESt3<-SolFitsMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt3$Phase<-"St"


SolFitsMetaPhase<-rbind(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)

rm(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)
```



# calibrated JVPSII 

```{r}

SolFitsMeta %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eLs, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eLs, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue),labeller = label_parsed) +
  theme_bw() 

SolFitsMetaPhase %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eLs, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eLs, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaPhase %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eLs, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eLs, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue, Phase, Run, E_days),labeller = label_parsed) +
  theme_bw() 
```

```{r}
SolFitsMetaLRC<-SolFitsMetaPhase %>%
  filter(Sig>0) %>% 
  filter(TauAv<4000) #few weitd outliers
```

# Convert Sig_m2psii to Sig_nm2psii and Sigdark_m2psii to Sigdark_nm2psii and calculated number of days when measurements were made

```{r convert Sigma}
SolFitsMetaLRC <- SolFitsMetaLRC %>%
mutate(Sig_nm2psii=Sig_m2psii*1000000000000000000) %>%
mutate(Sigdark_nm2psii=Sigdark_m2psii*1000000000000000000)
```

# Create preliminary plots 

```{r preliminary plot, fig.height = 5, fig.width = 8, warning = FALSE}
lab1=c(expression("PC-rich"), expression("PE-rich"))

SolFitsMetaLRC %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = Ex_WL, y = Sig), size = 3.5, show.legend = T) +
  #scale_colour_discrete(type=c("palegreen3", "brown4"), name="", labels = lab1) +
    ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase, Run, E_days),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 


```

# Create preliminary plots sig vs ActPAR

```{r preliminary plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))


SolFitsMetaLRC %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = Sig, colour = as.factor(Strain)), size = 3, show.legend = F) +
  geom_line(aes(x = ActPARCorr, y = Sig), size = 0.3, show.legend = F) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue, Phase, Run, E_days),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = TauAv, colour = as.factor(Strain)), size = 3, show.legend = F) +
  geom_line(aes(x = ActPARCorr, y = TauAv), size = 0.3, show.legend = F) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue, Phase, Run, E_days),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = qpOxbo, colour = as.factor(Strain)), size = 3, show.legend = F) +
  geom_line(aes(x = ActPARCorr, y = qpOxbo), size = 0.3, show.legend = F) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue, Phase, Run, E_days),labeller = label_parsed) +
  theme_bw() 


```


# Calculate Sigma mean from 3 replica measured on the same day 
# 6 replica b/c 3 replica * 2 values ("up" and "down")

```{r calculate Sigma mean from 3 replica measured on the same day}
SolFitsMetaLRC <- SolFitsMetaLRC %>%
  group_by(Strain, Ex_WL, Par_ue, Photoperiod, WL, O2, E_days, ObsDate, ActPARCorr, Phase, Run) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, PARPhotonDose_day, ObsDate, ObsTime, ObsDateTime, Sig, Sig_nm2psii, ActPARCorr, ActPARCorr_photonsm2s, Sigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_umol_eLs, E_days, TauAv, qpOxbo, ETRqpOxbo, Phase,
            meanSig_nm2psii = mean(Sig_nm2psii),
            sdSig_nm2psii = sd(Sig_nm2psii),
            
            meanTauAv = mean(TauAv),
            sdTauAv = sd(TauAv),
            
            meanqpOxbo = mean(qpOxbo),
            sdqpOxbo = sd(qpOxbo),
            
            meanJVPSII_umol_eLs = mean(JVPSII_umol_eLs),
            sdJVPSII_umol_eLs = sd(JVPSII_umol_eLs),
            
            meanETRqpOxbo = mean(ETRqpOxbo),
            sdETRqpOxbo = sd(ETRqpOxbo),
            
            meanSigdark_nm2psii = mean(Sigdark_nm2psii),
            sdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup() 
```

# Calculate Sigma Allmean measured on all days and Runs across different phase of growth 


```{r calculate Sigma mean across exp measurements}
SolFitsMetaLRC <- SolFitsMetaLRC %>%
  group_by(Strain, Ex_WL, Par_ue, Photoperiod, WL, O2, ActPARCorr, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL,  PARPhotonDose_day, ObsDate, ObsTime, ObsDateTime, Sig, Sig_nm2psii, meanSig_nm2psii, sdSig_nm2psii, meanSigdark_nm2psii, sdSigdark_nm2psii, ActPARCorr, ActPARCorr_photonsm2s, Sigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_umol_eLs, E_days, TauAv, qpOxbo, meanTauAv, sdTauAv, meanqpOxbo, sdqpOxbo, meanJVPSII_umol_eLs, sdJVPSII_umol_eLs, ETRqpOxbo, meanETRqpOxbo, sdETRqpOxbo, Phase,
            AllmeanSig_nm2psii = mean(meanSig_nm2psii),
            AllsdSig_nm2psii = sd(sdSig_nm2psii),
            
            AllmeanTauAv = mean(meanTauAv),
            AllsdTauAv = sd(sdTauAv),
            
            AllmeanqpOxbo = mean(meanqpOxbo),
            AllsdqpOxbo = sd(sdqpOxbo),
            
            AllmeanJVPSII_umol_eLs = mean(meanJVPSII_umol_eLs),
            AllsdJVPSII_umol_eLs = sd(sdJVPSII_umol_eLs),
            
            AllmeanETRqpOxbo = mean(meanETRqpOxbo),
            AllsdETRqpOxbo = sd(sdETRqpOxbo),
            
            AllmeanSigdark_nm2psii = mean(meanSigdark_nm2psii),
            AllsdSigdark_nm2psii = sd(sdSigdark_nm2psii)) %>%
  ungroup() 
```


# Create preliminary plots sig vs ActPAR

```{r preliminary plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, linetype=as.factor(WL)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(Par_ue, Phase),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanTauAv, colour = as.factor(WL)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanTauAv, linetype=as.factor(WL)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(Par_ue, Phase),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanqpOxbo, colour = as.factor(WL)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanqpOxbo, linetype=as.factor(WL)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(Par_ue, Phase),labeller = label_parsed) +
  theme_bw() 


```


# Create preliminary plots sig vs ActPAR

```{r preliminary plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, colour = as.factor(Phase)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, linetype=as.factor(Phase)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanTauAv, colour = as.factor(Phase)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanTauAv, linetype=as.factor(Phase)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue),labeller = label_parsed) +
  theme_bw() 


SolFitsMetaLRC %>%
  filter(Ex_WL == 535 | Ex_WL == 590) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanqpOxbo, colour = as.factor(Phase)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = AllmeanqpOxbo, linetype=as.factor(Phase)), size = 0.3, show.legend = T) +
  #geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  #ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  ggh4x::facet_nested(rows = vars(Strain, Ex_WL), cols = vars(WL, Par_ue),labeller = label_parsed) +
  theme_bw() 


```

# Create a df that WL correspond with Ex_WL

```{r}

```











# Create plot

```{r Create plot}

SolFitsMetaLRC %>%
  filter(Run == 56) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = meanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
    geom_line(aes(x = ActPARCorr, y = meanSig_nm2psii, colour = as.factor(WL)), show.legend = T) +
  ggh4x::facet_nested(rows = vars(Run, Strain, E_days, Ex_WL), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 

SolFitsMetaLRC %>%
  filter(Run == 59) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = meanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
  geom_line(aes(x = ActPARCorr, y = meanSig_nm2psii, colour = as.factor(WL)), show.legend = T) +
  ggh4x::facet_nested(rows = vars(Run, Strain, E_days, Ex_WL), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 
# 
# SolFitsMetaLRC %>%
#   filter(Run == 63) %>% 
#   ggplot() +
#   geom_point(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
#   ggh4x::facet_nested(rows = vars(Run, Strain, E_days), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
#   theme_bw() 
# 
# SolFitsMetaLRC %>%
#   filter(Run == 68) %>% 
#   ggplot() +
#   geom_point(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
#   ggh4x::facet_nested(rows = vars(Run, Strain, E_days), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
#   theme_bw() 
# 
# SolFitsMetaLRC %>%
#   filter(Run == 70) %>% 
#   ggplot() +
#   geom_point(aes(x = ActPARCorr, y = AllmeanSig_nm2psii, colour = as.factor(WL)), size = 3, show.legend = T) +
#   ggh4x::facet_nested(rows = vars(Run, Strain, E_days), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
#   theme_bw() 
```



```{r}
SolFitsMetaLRC$facetsExcitation<-c("Excitation~(nm)")
```



# Choosen only corresponding data

```{r}
# SolFitsMetaLRCTrimChoosen450<-SolFitsMetaLRCTrim %>% 
#   filter(WL == 450) %>%
#   filter(Ex_WL == 445) 
# SolFitsMetaLRCTrimChoosen470<-SolFitsMetaLRCTrim %>% 
#   filter(WL == 470) %>%
#   filter(Ex_WL == 470) 
# SolFitsMetaLRCTrimChoosen530<-SolFitsMetaLRCTrim %>% 
#   filter(WL == 530) %>%
#   filter(Ex_WL == 535)  
# SolFitsMetaLRCTrimChoosen620<-SolFitsMetaLRCTrim %>% 
#   filter(WL == 620) %>%
#   filter(Ex_WL == 590) 
#   
# SolFitsMetaLRCTrimChoosen<-rbind(SolFitsMetaLRCTrimChoosen450, SolFitsMetaLRCTrimChoosen470, SolFitsMetaLRCTrimChoosen530, SolFitsMetaLRCTrimChoosen620)
# 
# rm(SolFitsMetaLRCTrimChoosen450, SolFitsMetaLRCTrimChoosen470, SolFitsMetaLRCTrimChoosen530, SolFitsMetaLRCTrimChoosen620)

```



```{r fig.height = 8, fig.width = 6, warning = FALSE}
# ggp<-Sig/Tau/qp
# ggp
```

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_SigTauqp",".png",sep = "")), height=8, width= 6,  dpi = 300, limitsize = TRUE)
```

----------------------------------------------- ANOVA ------------------------------------


# Calculated Anova 

Sig_nm2psii
```{r calculated statistics}

Stat<-SolFitsMetaLRC %>% 
filter(Ex_WL == 535) 
Stat$WL <- factor(Stat$WL) 
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(Sig_nm2psii~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp535<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp535$Ex_WL<-535

Stat<-SolFitsMetaLRC %>%
  filter(Ex_WL == 590) 
Stat$WL <- factor(Stat$WL)
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(Sig_nm2psii~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp590$Ex_WL<-590

AnovaSig<-rbind(AnovaTest_qp535, AnovaTest_qp590)
rm(AnovaTest_qp535, AnovaTest_qp590)
```


TauAv
```{r calculated statistics}
Stat<-SolFitsMetaLRC %>% 
filter(Ex_WL == 535) 
Stat$WL <- factor(Stat$WL) 
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(TauAv~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp535<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp535$Ex_WL<-535

Stat<-SolFitsMetaLRC %>%
  filter(Ex_WL == 590) 
Stat$WL <- factor(Stat$WL)
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(TauAv~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp590$Ex_WL<-590

AnovaTauAv<-rbind(AnovaTest_qp535, AnovaTest_qp590)
rm(AnovaTest_qp535, AnovaTest_qp590)
```



qpOxbo
```{r calculated statistics}
Stat<-SolFitsMetaLRC %>% 
filter(Ex_WL == 535) 
Stat$WL <- factor(Stat$WL) 
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(qpOxbo~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp535<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp535$Ex_WL<-535

Stat<-SolFitsMetaLRC %>%
  filter(Ex_WL == 590) 
Stat$WL <- factor(Stat$WL)
Stat$Par_ue <- factor(Stat$Par_ue)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(qpOxbo~WL*Par_ue*Strain, data=Stat)
AnovaTest_qp590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_qp590$Ex_WL<-590

AnovaqpOxbo<-rbind(AnovaTest_qp535, AnovaTest_qp590)
rm(AnovaTest_qp535, AnovaTest_qp590)
```


# Save RDS that create stats and tables

```{r}
saveRDS(AnovaSig, file.path(TableRdsPath, paste(Project, "Anova_SigLRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(AnovaTauAv, file.path(TableRdsPath, paste(Project, "Anova_TauLRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(AnovaqpOxbo, file.path(TableRdsPath, paste(Project, "Anova_qpLRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```



----------------------------------------------------------------------------------------------------------------------
---------------------------------------------------------------------------------------------------------------------



------------------------------------------------ MetaData Catalog ------------------------------------------------------

# Read MetaData Catalog

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```


------------------------------------------------------# Add Turner Catalog--------------------------------------------------

# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL)) %>% 
  filter(TurChl_ugL<212354.754)  #outliers

```

# Merge Turner with CultureCatalog

```{r}
ChlDataMeta <- CultureCatalog %>% 
  left_join(., ChlData, by = c("SampleID"="SampleID")) %>% 
    mutate(Strain=case_when(Strain=="BA127R"~"PE-rich",
         Strain=="BA77G"~"PC-rich")) %>% 
  drop_na(TurChl_ugL)
```


# Calculate Chl mean from 3 technical replica

```{r}
#colnames(ChlDataMeta)

ChlDataMeta <- ChlDataMeta %>%
  group_by(Strain, WL, Par_ue, Run, SampleID, ObsDate) %>%
  summarize(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, PARPhotonDose_day, ObsDate, TurChl_ugL,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup() %>% 
  select(-c(TurChl_ugL)) %>% 
  unique()


ChlDataMeta <- ChlDataMeta %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup()
```


-------------------------------# Create df with phases of growth---------------------------------

```{r}
MultiCultiDataAll70ExpResup<-ChlDataMeta %>% 
  filter(E_days >= 14)  
MultiCultiDataAll70ExpResup$Phase<-"ExpResuply"

All70PCExp1<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days < 14)  
All70PCExp1$Phase<-"Exp"

All70PCExp2<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 8)  
All70PCExp2$Phase<-"Exp"

All70PCExp3<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp3$Phase<-"Exp"

All70PCExp4<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp4$Phase<-"Exp"

All70PCSt1<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 9 & E_days <=13)  
All70PCSt1$Phase<-"St"

All70PCSt2<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt2$Phase<-"St"

All70PCSt3<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt3$Phase<-"St"




All70PEExp1<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp1$Phase<-"Exp"

All70PEExp2<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp2$Phase<-"Exp"

All70PEExp3<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days < 14)  
All70PEExp3$Phase<-"Exp"

All70PEExp4<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp4$Phase<-"Exp"


All70PESt1<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt1$Phase<-"St"

All70PESt2<-ChlDataMeta %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt2$Phase<-"St"

All70PESt3<-ChlDataMeta %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt3$Phase<-"St"


ChlDataMetaPhase<-rbind(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)

rm(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)
```




# Create Preliminary plot

```{r preliminary plot}
ChlDataMetaPhase %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanTurChl_ugL)) +
  ggh4x::facet_nested(cols = vars(Par_ue, Phase), rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Calculate Big Chl mean from replica taken from the same phase - for now (some weird issue, cant merge them propery - fix this later Sylwia!!! - Ex_WL problem from solisense)

PC-rich do not match! I got only PE-rich - check this and fix this Sylwia!!!!!!!

```{r}
#colnames(ChlDataMeta)

ChlDataMetaPhase <- ChlDataMetaPhase %>%
  group_by(Strain, WL, Par_ue, Phase) %>%
  summarize(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, PARPhotonDose_day, ObsDate, meanTurChl_ugL,sdTurChl_ugL, E_days, Phase,
            AllmeanTurChl_ugL = mean(meanTurChl_ugL),
            AllsdTurChl_ugL = sd(sdTurChl_ugL)) %>%
  ungroup() %>%
  unique()


ChlDataMetaPhaseTrim <- ChlDataMetaPhase %>%
  select(-c(E_days, ObsDate, ExpDate, Run, SampleID)) %>%
  unique()
```
# Only for now - I choose only Ex_WL 445. 

```{r}
SolFitsMetaLRC445<-SolFitsMetaLRC %>% 
  filter(Ex_WL == 445) %>% 
  select(-c(Ex_WL))
```





# Merge Sigma with chlorophyll Turner data 
It is "bigger" df than SolFitsPigmentExp, b/c I have 3 replica for Turner

```{r}

# SolFitsMetaLRCTrim<-SolFitsMetaLRC %>% 
#   select(-c(ObsDate, ObsTime, ObsDateTime, E_days, Phase, ExpDate))


SolFitsExpStTurner <- ChlDataMetaPhaseTrim %>%
  full_join(., SolFitsMetaLRC445, by = c("Strain"="Strain", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day", "Phase"="Phase")) %>% 
  unique()

#"ObsDate"="ObsDate"
```

# Removed TurChl_ugL b/c I have already mean from 3 technical replica - smaller df

```{r}
# SolFitsExpStTurner<-SolFitsExpStTurner %>% 
#   select(-c(TurChl_ugL)) %>% 
#   unique()
```

# Create Preliminary plot

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurner %>%
  ggplot() +
  geom_point(aes(x = WL, y = AllmeanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = Sig_nm2psii, x = AllmeanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs, x = AllmeanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>%
  filter(Phase== "Exp") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs, x = AllmeanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain, E_days), cols = vars(WL, Par_ue, Phase, Run),labeller = label_parsed) +
  theme_bw()

```











--------------------------------------------------- MD Pico --------------------------------------

# IMPORT MD PICO CORRELATION DATA

```{r set project variables, warning = FALSE, echo = FALSE}
Project <- "BalticO2"
zip_file <- file.path("..", "Data", "RawData", "MDPico.zip")

# List files in the extracted folder with a ".txt" extension
CountFiles <- unzip(zip_file, list = TRUE)
CountFiles <- CountFiles[grepl(".csv$", CountFiles$Name), "Name"]
print(CountFiles)

FileID <- "ExperimentSummaryData"
FileEncode <- "UTF-8" 
HeaderRows <- 0
DelimCS <- ","
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)
  
  # Read the file using read.table
  data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
  
  # Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in CountFiles
MDPicoTidy <- CountFiles %>%
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

```{r tidy CountTidy}

MDPicoTidy <- MDPicoTidy %>% 
  select(-c("Concentration", "Group", "Compound", "CDateTime")) %>% # remove superfluous columns
  mutate(Filename = str_remove(string = Filename, pattern = ".csv")) %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../MDPico/")) %>%
  separate(Filename, into = c("ObsDate", "Project", "Initials",  "PlateNr", "IndStud", "Organism", "Count"), sep = "([\\/\\/\\_\\_\\_\\_\\_])", remove = FALSE) %>%
  select(-c("IndStud", "Organism", "Count")) %>% 
  mutate(ObsDate = ymd_hm(ObsDate)) 

```

Load MDPicoMetaData catalog
```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# this is the URL or ID of a Sheet readable by anyone (with a link)

MDPicoMetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1Lerp5u25kzBtaBbnOYElYqUP59cn68gJpxxayhnGdkw/edit#gid=0") %>%
  #mutate(Date = as.numeric(Date)) %>%
  mutate(Date = ymd_hm(`Date`)) %>%
  separate(Date, into = c("Date_count", "Time_count"), sep = " ", remove = FALSE) %>%
  mutate(Date_count = ymd(`Date_count`)) 
```


# Merge MD Pico and Culture catalog

```{r}
MDPicoMeta <- MDPicoMetaData %>%
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID")) %>% 
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich",
         Strain=="BA77G"~"PC-rich")) 
```


# Merge

```{r}
MDPicoAll <- MDPicoTidy %>%
  mutate(PlateNr = as.double(PlateNr)) %>%
  left_join(., MDPicoMeta, by = c("Well.Name" = "WellNumber", "PlateNr" = "PlateNumber")) %>% 
  drop_na(Strain)
```

```{r, warning = FALSE}
MDPicoAll <- MDPicoAll %>%
  mutate(culture_inocul_L = as.double(culture_inocul_L)) %>%
  mutate(CapAreaPercentage = as.double(CapAreaPercentage)) %>%

  mutate(CellmL_MDPico = (`Cell.Count` * (0.001/culture_inocul_L)) /(CapAreaPercentage/100)) %>%
  # mutate(cellsml = `cellsmlwithoutpercentage`/(CapAreaPercentage/100))
group_by(SampleID) %>%
  arrange(Date_count) %>%
  mutate(E_days = as.numeric((Date_count - ExpDate[1]))) %>%
ungroup() 
  
```


# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = E_days, y = CellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Par_ue, O2), cols = vars(Strain, WL), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Calculate cell count mean from 3 technical replica - wierd issue with ObsDate_Count - probably I need to use MDPico correlation

```{r}
#Date_count

MDPicoAll <- MDPicoAll %>%
  filter(E_days>4) %>% 
group_by(Strain, WL, Par_ue, Run) %>%

summarize(Well.Name, Cell.Count, Filename, ObsDate, PlateNr, PlateID, SampleID, Date, Date_count, Time_count, media_inocul_L, culture_inocul_L, CapAreaPercentage, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, ExpEndDate, E_days, CellmL_MDPico, 
          meanCellmL_MDPico = mean(CellmL_MDPico), 
          sdCellmL_MDPico = sd(CellmL_MDPico)) %>%
ungroup() %>%
  
  rename(Cell_Count=Cell.Count) %>% 
  rename(Well_Name=Well.Name) %>% 
  rename(MeasDate = ObsDate) %>% 
  rename(ObsDateTime = Date) %>% 
  rename(ObsDate_count = Date_count) %>% 
  rename(ObsTime_count = Time_count) %>% 
  rename(FilenameMDPico=Filename) 
```

```{r}
#colnames(MDPicoAll)

MDPicoAll <- MDPicoAll %>%
  select(c(Strain, WL, SampleID, Run, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, O2, meanCellmL_MDPico, sdCellmL_MDPico))
```

# Create Preliminary plot

```{r preliminary plot}
MDPicoAll %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(cols = vars(Par_ue), rows = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```


# Merge Sigma-Turner with MDPicoData data 

```{r}
SolFitsExpStTurnerMD <- MDPicoAll %>%
  full_join(., SolFitsExpStTurner, by = c("SampleID"="SampleID", "Run"="Run", "Strain"="Strain", "ExpDate"="ExpDate", "Par_ue"="Par_ue", "Photoperiod"="Photoperiod", 'O2'="O2", "WL"="WL", "PARPhotonDose_day"="PARPhotonDose_day")) %>% 
  #drop_na(Ex_WL) %>% 
  unique()

#colnames(SolFitsExpStTurnerMD)
```

```{r preliminary plot}
#colnames(SolFitsExpStTurner)

SolFitsExpStTurnerMD %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD %>%
  filter(WL!= "WW") %>% 
  ggplot() +
  geom_point(aes(y = Sig_nm2psii, x = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurnerMD %>%
  filter(Phase== "Exp") %>%
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs, x = meanCellmL_MDPico)) +
  ggh4x::facet_nested(rows = vars(Strain, E_days), cols = vars(WL, Par_ue, Phase, Run),labeller = label_parsed) +
  theme_bw()


SolFitsExpStTurner %>%
  filter(Phase== "Exp") %>% 
  ggplot() +
  geom_point(aes(y = JVPSII_umol_eLs, x = AllmeanTurChl_ugL)) +
  ggh4x::facet_nested(rows = vars(Strain, E_days), cols = vars(WL, Par_ue, Phase, Run),labeller = label_parsed) +
  theme_bw()


```

# Calculate cell per L - for JVPSII

```{r}
SolFitsExpStTurnerMD<-SolFitsExpStTurnerMD %>% 
  mutate(meanCellL_MDPico=meanCellmL_MDPico*1000) %>% 
  mutate(sdCellL_MDPico=sdCellmL_MDPico*1000)

#colnames(SolFitsExpStTurnerMD)
```


# Save Rds for further analysis

```{r save rds}
saveRDS(SolFitsExpStTurnerMD, file.path(DataOut, paste(Project, "Processed_SolisenseDataCorrHalfPAR.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
#colnames(SolFitsExpStTurnerMD)
```

# checking plot

```{r}
SolFitsExpStTurnerMD %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanJVPSII_umol_eLs), size = 2, show.legend = T) +
    geom_errorbar(aes(x = ActPARCorr, ymin = AllmeanJVPSII_umol_eLs - AllsdJVPSII_umol_eLs, ymax = AllmeanJVPSII_umol_eLs + AllsdJVPSII_umol_eLs, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
#colnames(SolFitsMetaLRC)

```
# Adding codes from apply cumulative diel uncalibrated JVPSII

# Calculate umol chl a

```{r}
SolFitsExpStTurnerMD<-SolFitsExpStTurnerMD %>%
  mutate(meanTurChl_umolL=meanTurChl_ugL*0.00112)
```


JVPSII per Turner e/Chl/s and per cell - e/cell/s (meanCellmL_MDPico; meanTurChl_ugL)


```{r}
#colnames(SolFitsExpStTurnerMD)

# JVPSII_ETRqpOxbo_FoSig = JVPSII_Par_ue

GrowthRateSol<-SolFitsExpStTurnerMD %>%
  # filter(WL!="WW") %>% 
  #   filter(WL != 405) %>%
  #   filter(WL != 660) %>%
  #   filter(WL != 730) %>%
  #Turner
  mutate(JVPSII_umol_eugChls = AllmeanJVPSII_umol_eLs/meanTurChl_ugL) %>% #umol e/ug ch/s
  #mutate(JVPSII_umol_eLs_HalfPar_ue_ugChl = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii/meanTurChl_ugL) %>% 
  
  mutate(JVPSII_umol_eumolChls = AllmeanJVPSII_umol_eLs/meanTurChl_umolL) %>% #umol e/umol ch/s
  #mutate(JVPSII_umol_eLs_HalfPar_ue_umolChl = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii/meanTurChl_umolL) %>% 
  
  #cell per L based on MC OD680 and pamas corr
  mutate(JVPSII_umol_eCells = AllmeanJVPSII_umol_eLs/meanCellL_MDPico) 
  #mutate(JVPSII_umol_eLs_HalfPar_ue_cell = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii/meanCellL_MDPico)  
```


# Choosen only corresponding data

```{r}
# SolFitsMetaLRCTrimChoosen450<-GrowthRateSol %>% 
#   filter(WL == 450) %>%
#   filter(Ex_WL == 445) 
# SolFitsMetaLRCTrimChoosen470<-GrowthRateSol %>% 
#   filter(WL == 470) %>%
#   filter(Ex_WL == 470) 
# SolFitsMetaLRCTrimChoosen530<-GrowthRateSol %>% 
#   filter(WL == 530) %>%
#   filter(Ex_WL == 535)  
# SolFitsMetaLRCTrimChoosen620<-GrowthRateSol %>% 
#   filter(WL == 660) %>%
#   filter(Ex_WL == 590) 
#   
# GrowthRateSolChoosen<-rbind(SolFitsMetaLRCTrimChoosen450, SolFitsMetaLRCTrimChoosen470, SolFitsMetaLRCTrimChoosen530, SolFitsMetaLRCTrimChoosen620)
# 
# rm(SolFitsMetaLRCTrimChoosen450, SolFitsMetaLRCTrimChoosen470, SolFitsMetaLRCTrimChoosen530, SolFitsMetaLRCTrimChoosen620)


```


calculate JVPSII per day
GrowthRateSol - all data e/chl/s
GrowthRateSolChoosen - e/chl/s for corresponding light
GrowthRateSoliExpDay - e/chl/d for corresponding light

```{r}

# JVPSII_ETRqpOxbo_FoSig

GrowthRateSoliExpDay<-GrowthRateSol %>% 
  mutate(JVPSII_umol_eugChls_day = JVPSII_umol_eugChls*3600*Photoperiod/2) %>%
  #mutate(JVPSII_umol_eLs_HalfPar_ue_ugChl_day = JVPSII_umol_eLs_HalfPar_ue_ugChl*3600*Photoperiod/2) %>%
  mutate(JVPSII_umol_eumolChls_day = JVPSII_umol_eumolChls*3600*Photoperiod/2) %>% 
  #mutate(JVPSII_umol_eLs_HalfPar_ue_umolChl_day = JVPSII_umol_eLs_HalfPar_ue_umolChl*3600*Photoperiod/2) %>% 
  mutate(JVPSII_umol_eCells_day = JVPSII_umol_eCells*3600*Photoperiod/2) %>% 
  #mutate(JVPSII_umol_eLs_HalfPar_ue_cell_day = JVPSII_umol_eLs_HalfPar_ue_cell*3600*Photoperiod/2) %>% 
  unique()

```

# Think Sylwia about JVPSII mean!!! 

```{r}

# MCGrowthJVPSIISPmean<-GrowthRateSoliExpDay2 %>% 
#  
#   group_by(Strain, O2, Oxygen, WL, Ex_WL) %>%
#   summarize(Strain, Par_ue, Photoperiod, O2, Oxygen, WL, Ex_WL, deltaOD_Lmu_se, deltaOD_Lmu_corr, JVPSII_umol_eLs_Par_ue_ugChl_day, JVPSII_umol_eLs_Par_ue_umolChl_day, JVPSII_umol_eLs_Par_ue_cell_day, 
# JVPSII_umol_eLs_HalfPar_ue_ugChl_day, JVPSII_umol_eLs_HalfPar_ue_umolChl_day, JVPSII_umol_eLs_HalfPar_ue_cell_day, 
#     
#             meanJVPSII_umol_eLs_Par_ue_ugChl_day = mean(JVPSII_umol_eLs_Par_ue_ugChl_day),
#             sdJVPSII_umol_eLs_Par_ue_ugChl_day = sd(JVPSII_umol_eLs_Par_ue_ugChl_day),
#             
#             meanJVPSII_umol_eLs_Par_ue_umolChl_day = mean(JVPSII_umol_eLs_Par_ue_umolChl_day),
#             sdJVPSII_umol_eLs_Par_ue_umolChl_day = sd(JVPSII_umol_eLs_Par_ue_umolChl_day),
#             
#             meanJVPSII_umol_eLs_Par_ue_cell_day = mean(JVPSII_umol_eLs_Par_ue_cell_day),
#             sdJVPSII_umol_eLs_Par_ue_cell_day = sd(JVPSII_umol_eLs_Par_ue_cell_day),
#             
#             
#             meanJVPSII_umol_eLs_HalfPar_ue_ugChl_day = mean(JVPSII_umol_eLs_HalfPar_ue_ugChl_day),
#             sdJVPSII_umol_eLs_HalfPar_ue_ugChl_day = sd(JVPSII_umol_eLs_HalfPar_ue_ugChl_day),
#             
#             meanJVPSII_umol_eLs_HalfPar_ue_umolChl_day = mean(JVPSII_umol_eLs_HalfPar_ue_umolChl_day),
#             sdJVPSII_umol_eLs_HalfPar_ue_umolChl_day = sd(JVPSII_umol_eLs_HalfPar_ue_umolChl_day),
#             
#             meanJVPSII_umol_eLs_HalfPar_ue_cell_day = mean(JVPSII_umol_eLs_HalfPar_ue_cell_day),
#             sdJVPSII_umol_eLs_HalfPar_ue_cell_day = sd(JVPSII_umol_eLs_HalfPar_ue_cell_day)) %>%
#   ungroup()
#   
# 
# MCGrowthJVPSIISPmean$facetsStrain <- 'Strain'
```





# Cumulative uncalibrated JVPSII vs ActPAR - e/chl/d

```{r}

GrowthRateSoliExpDay %>%
  filter(Phase == "Exp") %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls_day), size = 3, show.legend = T) +
  #geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls_day), size = 0.3, show.legend = T) +
  # geom_errorbar(aes(x = ActPARCorr, ymin = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii - AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, ymax = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii + AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  # geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  # scale_fill_identity() +
  # scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  # scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  # scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  # scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  # scale_x_continuous(breaks=seq(0, 800, by = 200)) +
  # coord_cartesian(ylim = c(0, 10), xlim = c(0, 800)) +
  #labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  ggh4x::facet_nested(cols = vars(WL, Par_ue, Run, Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```
# Cumulative uncalibrated JVPSII per chl per s

```{r}

GrowthRateSol %>%
    filter(Phase == "Exp") %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(Phase)), size = 3, show.legend = T) +
  #geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  # geom_errorbar(aes(x = ActPARCorr, ymin = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii - AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, ymax = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii + AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  # geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  # scale_fill_identity() +
  # scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  # scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  # scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  # scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  # scale_x_continuous(breaks=seq(0, 800, by = 200)) +
  # coord_cartesian(ylim = c(0, 10), xlim = c(0, 800)) +
  #labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  ggh4x::facet_nested(cols = vars(WL, Par_ue, Run, Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

-------- Harrison Platt ---------------


# Estimated Harrison & Platt, 1986 fit - for all uE and each uE separately

```{r platt fit}
#Harrison & Platt, 1986
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

MCGrowthSPAllFit21 <- GrowthRateSol %>%   
  filter(O2 == 21) %>% 
  nest(data = -c("Strain", "Par_ue", "WL")) %>%  
  mutate(GRCplatt_Model = map(data, ~nlsLM(JVPSII_umol_eumolChls ~ grcplatt(I = ActPARCorr, a, b, Pmax),
         data = .x,start = list(a = 0.1/90, b = 0.1/200, Pmax = 0.2),lower = c(0, 0, 0)))) %>%    
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),          
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),          
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance)))
GRCplatt_PredictGrowthAll21 <- MCGrowthSPAllFit21 %>% 
  unnest(GRCplatt_Predict)%>% 
  unnest(GRCplatt_Param)



```


```{r}

GrowthRateSol %>%
  filter(Phase == "Exp" | Phase == "ExpResupply") %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(Phase)), size = 3, show.legend = T) +
  #geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  
  geom_line(aes(ActPARCorr, .fitted), colour = "blue", linetype = "solid", size = 0.3, show.legend = F, GRCplatt_PredictGrowthAll21) +
  # geom_line(aes(ActPARCorr, .fitted), colour = "blue", linetype = "solid", size = 0.3, show.legend = F, GRCplatt_PredictGrowthAll0) +
  
  # geom_errorbar(aes(x = ActPARCorr, ymin = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii - AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, ymax = AllmeanJVPSII_ETRqpOxbo_FoSigmax_m2psii + AllsdJVPSII_ETRqpOxbo_FoSigmax_m2psii, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  # geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  # scale_fill_identity() +
  # scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  # scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  # scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  # scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  # scale_x_continuous(breaks=seq(0, 800, by = 200)) +
  # coord_cartesian(ylim = c(0, 10), xlim = c(0, 800)) +
  #labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

# Fancy plot

```{r}

lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))

MultiCultiGrowth1PC21<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21)
MultiCultiGrowth1PE21<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 21)
  
MultiCultiGrowth1PC0<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0)
MultiCultiGrowth1PE0<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL != "WW") %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 0)


CalibJVPSIIpers<-GrowthRateSol %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "palegreen3", shape = 1, size = 3, show.legend = F, MultiCultiGrowth1PC21) +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "brown4", shape = 1, size = 3, show.legend = F, MultiCultiGrowth1PE21) +

  
  # geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eLs_Par_ue_umolChl, linetype = as.factor(O2)), size = 0.3, show.legend = F) +
  
  geom_line(aes(ActPARCorr, .fitted), colour = "blue", linetype = "dashed", size = 0.3, show.legend = F, GRCplatt_PredictGrowthAll21) +

  
  #geom_errorbar(aes(x = ActPARCorr, ymin = JVPSII_umol_eLs_Par_ue_umolChl - JVPSII_umol_eLs_Par_ue_umolChl, ymax = AllmeanJVPSII_umol_eLs + AllsdJVPSII_umol_eLs, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.4) +
  #geom_text(data=data_textA, aes(x=750, y=0.90, label=label), size=6, parse = TRUE) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  scale_y_continuous(breaks=seq(0, 1.0, by = 0.2)) +
  scale_x_continuous(breaks=seq(0, 900, by = 300)) +
  coord_cartesian(ylim = c(0, 1.0), xlim = c(0, 900)) +
  #labs(y=expression(paste(Uncalib_JV,""["PSII"]*"")), x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  labs(y = ""~italic(JV)~""["PSII"]*" (µmol"~e^-~""~µmol~Chl~italic(a)~""^-1~""~s^-1~")", x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +

  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.90),
        legend.text = element_text(size=10))
CalibJVPSIIpers

```
```{r fig.height = 8, fig.width = 6, warning = FALSE}
# ggp<-CalibJVPSIIpers/JVPSIIGrowth
# ggp
```

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_jvpsii",".png",sep = "")), height=8, width= 6, dpi = 300, limitsize = TRUE)
```


# Stats jvpsii e/chl/s

JVPSII
```{r calculated statistics}
Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 445) %>%
  filter(WL == "450")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_jvpsii445<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_jvpsii445$Ex_WL<-445

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 470) %>%
  filter(WL == "470")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_jvpsii470<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_jvpsii470$Ex_WL<-470

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 535) %>%
  filter(WL == "530")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_jvpsii535<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_jvpsii535$Ex_WL<-535

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 590) %>%
  filter(WL == "620")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_jvpsii590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_jvpsii590$Ex_WL<-590

Anovajvpsii<-rbind(AnovaTest_jvpsii445, AnovaTest_jvpsii470, AnovaTest_jvpsii535, AnovaTest_jvpsii590)
rm(AnovaTest_jvpsii445, AnovaTest_jvpsii470, AnovaTest_jvpsii535, AnovaTest_jvpsii590)
```



# Save RDS that create stats and tables

```{r}
saveRDS(Anovajvpsii, file.path(TableRdsPath, paste(Project, "Anova_jvpsiiLRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


-------------------------------------------- Doug Chl per PSII --------------------

GrowthRateSol - all data e/chl/s
GrowthRateSolChoosen - e/chl/s for corresponding light
GrowthRateSoliExpDay - e/chl/d for corresponding light

```{r electron PSII per s}

GrowthRateSol %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = ETRqpOxbo, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 

GrowthRateSol %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(WL, Par_ue), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```


```{r electron PSII per s}

GrowthRateSolChoosen %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = ETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 

GrowthRateSolChoosen %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

```{r electron PSII per s}

GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 445) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 535) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 590) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  #filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  filter(Ex_WL == 445) %>%
  #filter(Strain == "PC-rich") %>% 
  ggplot() +
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 

GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich") %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain, WL), labeller = label_parsed) +
  theme_bw()
```

# mean of ActPAR only for plot

```{r calculate Sigma mean from 3 replica measured on the same day}

GrowthRateSolPlot <- GrowthRateSol %>%
    filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
    mutate(PSIIChla = AllmeanETRqpOxbo/JVPSII_umol_eumolChls) 
  
GrowthRateSolPlot2 <- GrowthRateSolPlot %>%
  group_by(Strain, WLNum, WL, O2, Oxygen) %>%
  summarize(GrowthRateSolPlot, 
            meanPSIIChla = mean(PSIIChla)) %>%
  ungroup() 

```



```{r}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))

MultiCultiGrowth1PC21<-GrowthRateSol %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21)
MultiCultiGrowth1PE21<-GrowthRateSol %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 21)
  
MultiCultiGrowth1PC0<-GrowthRateSol %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0)
MultiCultiGrowth1PE0<-GrowthRateSol %>% 
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 0)


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) %>%
  #filter(Strain == "PC-rich") %>% 
  ggplot() +
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 4, show.legend = T) +
  #geom_line(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls, linetype = as.factor(O2)), show.legend = F) +
    
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls), colour = "palegreen3", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PC21) +
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls), colour = "brown4", shape = 1, size = 4, show.legend = F, MultiCultiGrowth1PE21) +
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls), colour = "palegreen3", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PC0) +
  geom_point(aes(x = WL, y = AllmeanETRqpOxbo/JVPSII_umol_eumolChls), colour = "brown4", shape = 16, size = 4, show.legend = F, MultiCultiGrowth1PE0) +
  
  
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  
  #stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.080, alpha = 0.5) +
  #scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  
  scale_y_continuous(breaks=seq(0, 1200, by = 300)) +
  coord_cartesian(ylim = c (0, 1300)) +
  labs(y = "Chl" ~italic(a)~ " to PSII (mole:mole)", x = "Growth waveband (nm)") +
  ggh4x::facet_nested(rows = vars(Strain), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.94),
        legend.text = element_text(size=10))
  
```


# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_PSIIChla",".png",sep = "")), height=4, width= 5,  dpi = 300, limitsize = TRUE)
```


--------------- ANOVA ------------


# Calculated Anova and Tukey test

```{r calculated statistics}
GrowthRateSol2<-GrowthRateSol %>% 
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445) 
  #mutate(ChlPSII= AllmeanETRqpOxbo/JVPSII_umol_eumolChls)


MCGrowthRateStats<-GrowthRateSol2 

MCGrowthRateStats$O2 <- factor(MCGrowthRateStats$O2)
MCGrowthRateStats$WL <- factor(MCGrowthRateStats$WL)
MCGrowthRateStats$Strain <- factor(MCGrowthRateStats$Strain)

# Two way Anova with interactions
model<-aov(AllmeanETRqpOxbo/JVPSII_umol_eumolChls~O2*WL*Strain, data=MCGrowthRateStats)
AnovaTest_ChlaPSII<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_GrowthRate<-TukeyHSD(model, which = c("O2", "WL", "Strain"))


```


# Save RDS that create stats and tables

```{r}
saveRDS(AnovaTest_ChlaPSII, file.path(TableRdsPath, paste(Project, "Anova_ChlaPSII.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


```{r electron PSII per s}

GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 445) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 535) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(Ex_WL== 590) %>% 
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL, WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

------------------------------- proper plots for JVPSII vs ActinicPAR e/chl/s ------------------------------


```{r}
lab1=c(expression("PC-rich"), expression("PE-rich"))
lab2=c(expression("2.5 µM"), expression("250 µM"))


drectblue <- data.frame(Ex_WL = c("445", "445"), Strain = c("PC-rich", "PE-rich"), WL = c("450", "450"), x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))

drectsemiblue <- data.frame(Ex_WL = c("470", "470"), Strain = c("PC-rich", "PE-rich"), WL = c("470", "470"), x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))

drectgreen <- data.frame(Ex_WL = c("535", "535"), Strain = c("PC-rich", "PE-rich"), WL = c("530", "530"), x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))

drectred <- data.frame(Ex_WL = c("590", "590"), Strain = c("PC-rich", "PE-rich"), WL = c("620", "620"), x1=c(-Inf), x2=c(Inf), y1=c(-Inf), y2=c(Inf))


MultiCultiGrowth1PC21<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 21)
MultiCultiGrowth1PE21<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 21)
  
MultiCultiGrowth1PC0<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  filter(Strain == "PC-rich") %>% 
  filter(O2 == 0)
MultiCultiGrowth1PE0<-GrowthRateSol %>% 
    mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  filter(Strain == "PE-rich") %>% 
    filter(O2 == 0)


GrowthRateSol %>%
  mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
  #filter(Strain == "PC-rich") %>% 
  #filter(O2 == 0) %>% 
  filter(WL == 450 | WL == 530 |  WL == 620 | WL == 470) %>%
  filter(Ex_WL == 445 | Ex_WL == 535 | Ex_WL == 590 | Ex_WL == 470) %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, shape = as.factor(O2)), size = 3, show.legend = T) +
  #geom_point(aes(x = ActPARCorr, y = Sig_nm2psii, colour = as.factor(Strain)), size = 1, alpha = 0.2, show.legend = F) +
  
    geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "palegreen3", shape = 1, size = 3, show.legend = F, MultiCultiGrowth1PC21) +
    geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "brown4", shape = 1, size = 3, show.legend = F, MultiCultiGrowth1PE21) +
    geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "palegreen3", shape = 16, size = 3, show.legend = F, MultiCultiGrowth1PC0) +
    geom_point(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls), colour = "brown4", shape = 16, size = 3, show.legend = F, MultiCultiGrowth1PE0) +
  
  # geom_errorbar(aes(x = ActPARCorr, ymin = JVPSII_umol_eLs_Par_ue_umolChl - AllsdJVPSII_umol_eLs, ymax = AllmeanJVPSII_umol_eLs + AllsdJVPSII_umol_eLs, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  
  geom_line(aes(x = ActPARCorr, y = JVPSII_umol_eumolChls, linetype = as.factor(O2)), size = 0.3, show.legend = T) +
  #geom_line(aes(x = ActPARCorr, y = svr_pred, linetype = as.factor(O2)), size = 0.6, show.legend = T, MCDataHourSVR) +
  
  
  
  geom_vline(xintercept = 90, linetype = "dotted", size = 0.7) +
  
  geom_rect(data=drectblue, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="steelblue3", alpha = 0.2, size=1) +
  geom_rect(data=drectsemiblue, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2),  fill="lightseagreen", alpha = 0.2, size=1) +
  
  geom_rect(data=drectgreen, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="limegreen", alpha = 0.2, size=1) +
  geom_rect(data=drectred, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill="coral", alpha = 0.2, size=1) +
  
  scale_fill_identity() +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab2) +
  scale_shape_manual(values = c(16, 1), name="", labels = lab2) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab2) +

  scale_x_continuous(breaks=seq(0, 900, by = 300)) +
  coord_cartesian(xlim = c(0, 900)) +
  
  labs(y = ""~italic(JV)~""["PSII"]*" (µmol"~e^-~""~µmol~Chl~italic(a)~""^-1~""~s^-1~")", x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  
  #labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain, WL), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.10,0.94),
        legend.text = element_text(size=10))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_CalibJVPSII_eChls",".png",sep = "")), height=8, width= 6,  dpi = 300, limitsize = TRUE)
```

----------------------------------------------- ANOVA ------------------------------------


# Calculated Anova 

JVPSII_umole_umolChl_s

```{r calculated statistics}
Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 445) %>%
  filter(WL == "450")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_JVPSII445<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_JVPSII445$Ex_WL<-445

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 470) %>%
  filter(WL == "470")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_JVPSII470<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_JVPSII470$Ex_WL<-470

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 535) %>%
  filter(WL == "530")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_JVPSII535<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_JVPSII535$Ex_WL<-535

Stat<-GrowthRateSolChoosen %>%
  filter(Ex_WL == 590) %>%
  filter(WL == "620")
Stat$O2 <- factor(Stat$O2)
Stat$ActPARCorr <- factor(Stat$ActPARCorr)
Stat$Strain <- factor(Stat$Strain)
# Three way Anova with interactions
model<-aov(JVPSII_umol_eumolChls~O2*ActPARCorr*Strain, data=Stat)
AnovaTest_JVPSII590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_JVPSII590$Ex_WL<-590

AnovaJVPSII<-rbind(AnovaTest_JVPSII445, AnovaTest_JVPSII470, AnovaTest_JVPSII535, AnovaTest_JVPSII590)
rm(AnovaTest_JVPSII445, AnovaTest_JVPSII470, AnovaTest_JVPSII535, AnovaTest_JVPSII590)
```



# Save RDS that create stats and tables

```{r}

saveRDS(AnovaJVPSII, file.path(TableRdsPath, paste(Project, "Anova_JVPSII_eChlsLRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```













# Fit LRC for JVPSII to allow selection of specific JVPSII for different growth light levels.

```{r}
# lrcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}
# 
# 
# SolFitsMetaLRC <- SolFitsMeta %>%
#   nest(data = -c("SampleID", "Run", "Strain" ,"ExpDate","Par_ue", "Photoperiod", "O2", "WL", "MC", "Tube","Ex_WL","LightShape", "ExpEndDate", "PARPhotonDose_day", "ObsDate", "E_days")) %>% #head(50) %>% 
#   mutate(lrcplatt_Model = map(data, possibly(~nlsLM(JVPSII_umol_eLs ~ lrcplatt(I = ActPARCorr, a, b, Pmax),
#          data = .x,
#          control = list(maxiter = 100),
#          start = list(a = 0.1, b = 0.01, Pmax = 3), lower = c(0, 0, 0))))) %>%
#   mutate(lrcplatt_Param = map(lrcplatt_Model, tidy),
#          lrcplatt_Predict = map(lrcplatt_Model, possibly(augment)),
#          lrcplatt_Glance = map(lrcplatt_Model, possibly(glance)))

```

Use Peak Par_ue and 1/2 Peak Par_ue to estimate growth JVPSII for each combination
-use 'Pluck' to reach into lrcplatt_Predict to get a, b, Pmax; or
-unnest, pivot wider to get a, b, Pmax

```{r growth light JVPSII}

# SolFitsMetaLRCGrowth <- SolFitsMetaLRC |>
#   unnest(lrcplatt_Param) |>
#   select(-c(statistic, p.value, lrcplatt_Predict, lrcplatt_Glance)) |> #remove (temporarily) to make pivot_wider easier
#   pivot_wider(names_from = term, values_from = c(estimate, std.error)) |>
#   mutate(JVPSII_umol_eLs_Par_ue = lrcplatt(I = Par_ue, a = estimate_a, estimate_b, estimate_Pmax),
#          JVPSII_umol_eLs_HalfPar_ue = lrcplatt(I = (0.5*Par_ue), a = estimate_a, estimate_b, estimate_Pmax))
# 
#  
# head(SolFitsMetaLRCGrowth) 
```










Set up R codes for Greek letters

\u0391  Α   Greek Capital Letter Alpha
\u0392  Β   Greek Capital Letter Beta
\u0393  Γ   Greek Capital Letter Gamma
\u0394  Δ   Greek Capital Letter Delta
\u0395  Ε   Greek Capital Letter Epsilon
\u0396  Ζ   Greek Capital Letter Zeta
\u0397  Η   Greek Capital Letter Eta
\u0398  Θ   Greek Capital Letter Theta
\u0399  Ι   Greek Capital Letter Iota
\u039A  Κ   Greek Capital Letter Kappa
\u039B  Λ   Greek Capital Letter Lambda
\u039C  Μ   Greek Capital Letter Mu
\u039D  Ν   Greek Capital Letter Nu
\u039E  Ξ   Greek Capital Letter Xi
\u039F  Ο   Greek Capital Letter Omicron
\u03A0  Π   Greek Capital Letter Pi
\u03A1  Ρ   Greek Capital Letter Rho
\u03A3  Σ   Greek Capital Letter Sigma
\u03A4  Τ   Greek Capital Letter Tau
\u03A5  Υ   Greek Capital Letter Upsilon
\u03A6  Φ   Greek Capital Letter Phi
\u03A7  Χ   Greek Capital Letter Chi
\u03A8  Ψ   Greek Capital Letter Psi
\u03A9  Ω   Greek Capital Letter Omega
\u03B1  α   Greek Small Letter alpha
\u03B2  β   Greek Small Letter beta
\u03B3  γ   Greek Small Letter gamma
\u03B4  δ   Greek Small Letter delta
\u03B5  ε   Greek Small Letter epsilon
\u03B6  ζ   Greek Small Letter zeta
\u03B7  η   Greek Small Letter eta
\u03B8  θ   Greek Small Letter theta
\u03B9  ι   Greek Small Letter iota
\u03BA  κ   Greek Small Letter kappa
\u03BB  λ   Greek Small Letter lambda
\u03BC  μ   Greek Small Letter mu
\u03BD  ν   Greek Small Letter nu
\u03BE  ξ   Greek Small Letter xi
\u03BF  ο   Greek Small Letter omicron
\u03C0  π   Greek Small Letter pi
\u03C1  ρ   Greek Small Letter rho
\u03C2  ς   Greek Small Letter final sigma
\u03C3  σ   Greek Small Letter sigma
\u03C4  τ   Greek Small Letter tau
\u03C5  υ   Greek Small Letter upsilon
\u03C6  φ   Greek Small Letter phi
\u03C7  χ   Greek Small Letter chi
\u03C8  ψ   Greek Small Letter psi
\u03C9  ω   Greek Small Letter omega





