---
title: "Process_OlisJazEmData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_OlisJazEmData.Rmd processes and combines BalticPhotoperiod_Imported_JazEmData.Rds from Data/ImportedData/ImportedJazEmData folder and BalticPhotoperiod_Imported_OlisData.Rds from Data/ImportedData/ImportedOlisData folder. This .Rmd generates BalticPhotoperiod_Processed_OlisSpectraAll.Rds and BalticPhotoperiod_Processed_OlisSpectraTidy.Rds (both stored in Data/ProcessedData/ProcessedOlisJazData folder) and 1 plot (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 


library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggspectra)
library(ggpubr)
library(caret)
library(photobiologyWavebands)
library(reshape2)
library(photobiology)
library(gcookbook)

library(googledrive)
library(googlesheets4)
library(readxl)
library(tidyverse)
library(lubridate)
library("patchwork") # merging plots
```

```{r set project variables}
Project <- "BalticCCA"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData")
DataInOlis <- file.path("..", "Data", "ImportedData", "ImportedOlisData", fsep = .Platform$file.sep)
DataInJaz <- file.path("..", "Data", "ImportedData", "ImportedJazEmData", fsep = .Platform$file.sep)


FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read imported Olis and Jaz files + growth curve for different phases

```{r exported Rmd only first time in session}
list.files(path = DataInOlis, pattern = Project, full.names = TRUE)
list.files(path = DataInJaz, pattern = Project, full.names = TRUE)

```

```{r read imported Olis file}
OLISSpectraFile <- "../Data/ImportedData/ImportedOlisData/BalticCCA_Imported_OlisData.Rds"
OLISSpectraFileName <- str_split(string = OLISSpectraFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
OLISSpectra <- readRDS(OLISSpectraFile)  %>%
  ungroup()

JazFile <- "../Data/ImportedData/ImportedJazEmData/BalticCCA_Imported_JazEmData.Rds"
JazFileName <- str_split(string = JazFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
JazData <- readRDS(JazFile)  %>%
  ungroup()

```

# Preparing df for further analysis

```{r}
JazData<-JazData %>% 
  #filter(WL != "WW") %>% 
  select(-c(MCMeasuredPar_uE, MCSetPar_uE))
```


# Normalize Jaz emission to 405 nm

```{r Normalization Jaz emission at 405}
EmissionJaz405 <- JazData %>%
  filter(WL==405) %>% 
  filter(MCEm_nm == 393) %>%
  mutate(EmJaz393 = Emission) %>%
  select(EmJaz393) 

JazDataRoundMeta405 <- JazData %>%
  filter(WL==405) %>% 
  cross_join(., EmissionJaz405) %>%
  mutate(EmNormJaz393 = Emission / EmJaz393)

rm(EmissionJaz405)
```

# Normalize Jaz emission to 450 nm

```{r Normalization Jaz emission at 450}
EmissionJaz450 <- JazData %>%
  filter(WL==450) %>% 
  filter(MCEm_nm == 441) %>%
  mutate(EmJaz441 = Emission) %>%
  select(EmJaz441)

JazDataRoundMeta450 <- JazData %>%
  filter(WL==450) %>% 
  cross_join(., EmissionJaz450) %>%
  mutate(EmNormJaz441 = Emission / EmJaz441)

rm(EmissionJaz450)
```

# Normalize Jaz emission to 470 nm

```{r Normalization Jaz emission at 470}
EmissionJaz470 <- JazData %>%
  filter(WL==470) %>% 
  filter(MCEm_nm == 469) %>%
  mutate(EmJaz469 = Emission) %>%
  select(EmJaz469) 

JazDataRoundMeta470 <- JazData %>%
  filter(WL==470) %>% 
  cross_join(., EmissionJaz470) %>%
  mutate(EmNormJaz469 = Emission / EmJaz469)

rm(EmissionJaz470)
```

# Normalize Jaz emission to 530 nm

```{r Normalization Jaz emission at 530}
EmissionJaz530 <- JazData %>%
  filter(WL==530) %>% 
  filter(MCEm_nm == 521) %>%
  mutate(EmJaz521 = Emission) %>%
  select(EmJaz521)

JazDataRoundMeta530 <- JazData %>%
  filter(WL==530) %>% 
  cross_join(., EmissionJaz530) %>%
  mutate(EmNormJaz521 = Emission / EmJaz521)

rm(EmissionJaz530)
```

# Normalize Jaz emission to 620 nm

```{r Normalization Jaz emission at 620}
EmissionJaz620 <- JazData %>%
  filter(WL==620) %>% 
  filter(MCEm_nm == 612) %>%
  mutate(EmJaz612 = Emission) %>%
  select(EmJaz612) 

JazDataRoundMeta620 <- JazData %>%
  filter(WL==620) %>% 
  cross_join(., EmissionJaz620) %>%
  mutate(EmNormJaz612 = Emission / EmJaz612)

rm(EmissionJaz620)
```

# Normalize Jaz emission to 660 nm

```{r Normalization Jaz emission at 660}
EmissionJaz660 <- JazData %>%
  filter(WL==660) %>% 
  filter(MCEm_nm == 647) %>%
  mutate(EmJaz647 = Emission) %>%
  select(EmJaz647)

JazDataRoundMeta660 <- JazData %>%
  filter(WL==660) %>% 
  cross_join(., EmissionJaz660) %>%
  mutate(EmNormJaz647 = Emission / EmJaz647)

rm(EmissionJaz660)
```

# Normalize Jaz emission to 730 nm

```{r Normalization Jaz emission at 730}
EmissionJaz730 <- JazData %>%
  filter(WL==730) %>% 
  filter(MCEm_nm == 722) %>%
  mutate(EmJaz722 = Emission) %>%
  select(EmJaz722) 

JazDataRoundMeta730 <- JazData %>%
  filter(WL==730) %>% 
  cross_join(., EmissionJaz730) %>%
  mutate(EmNormJaz722 = Emission / EmJaz722)

rm(EmissionJaz730)
```

# Normalize Jaz emission to WW

```{r Normalization Jaz emission at WW}
EmissionJazWW <- JazData %>%
  filter(WL== "WW") %>%
  filter(MCEm_nm == 600) %>%
  mutate(EmJaz600 = Emission) %>%
  select(EmJaz600) 

JazDataRoundMetaWW <- JazData %>%
  filter(WL== "WW") %>%
  cross_join(., EmissionJazWW) %>%
  mutate(EmNormJaz600 = Emission / EmJaz600)

rm(EmissionJazWW)
```
# Merge df to have all WL

```{r}
JazDataRoundMeta1 <- JazDataRoundMeta730 %>%
  full_join(., JazDataRoundMetaWW, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz"))
 
JazDataRoundMeta2 <- JazDataRoundMeta1 %>%
  full_join(., JazDataRoundMeta660, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta3 <- JazDataRoundMeta2 %>%
  full_join(., JazDataRoundMeta620, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta4 <- JazDataRoundMeta3 %>%
  full_join(., JazDataRoundMeta530, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta5 <- JazDataRoundMeta4 %>%
  full_join(., JazDataRoundMeta470, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta6 <- JazDataRoundMeta5 %>%
  full_join(., JazDataRoundMeta450, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 

JazDataRoundMeta <- JazDataRoundMeta6 %>%
  full_join(., JazDataRoundMeta405, by = c("FilenameJaz"= "FilenameJaz", "WL" = "WL", "MCEm_nm" = "MCEm_nm", "Emission" = "Emission", "MC"="MC", "EmMax_nm"="EmMax_nm", "ObsDateJaz"="ObsDateJaz")) 


rm(JazDataRoundMeta1, JazDataRoundMeta2, JazDataRoundMeta3, JazDataRoundMeta4, JazDataRoundMeta5, JazDataRoundMeta6, JazDataRoundMeta405, JazDataRoundMeta450, JazDataRoundMeta470, JazDataRoundMeta530, JazDataRoundMeta620, JazDataRoundMeta660, JazDataRoundMeta730, JazDataRoundMetaWW)
```

# Prepare OlisSpectra



```{r}
JazDataRoundMeta<-JazDataRoundMeta %>% 
  select(-c(MC, Emission))
```


# Merge Olis and Jaz data

```{r combine Olis spectra and Jaz data}
OLISSpectraMeta <- OLISSpectra %>%
  full_join(., JazDataRoundMeta, by = c("nm" = "MCEm_nm", "WL" = "WL")) %>%
  unique()
```

# Estimate PUR

```{r estimate PUR}
OLISSpectraMetaPUR405 <- OLISSpectraMeta %>%
  filter(WL==405) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz393)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz393)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR450 <- OLISSpectraMeta %>%
  filter(WL==450) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz441)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz441)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR470 <- OLISSpectraMeta %>%
  filter(WL==470) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz469)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz469)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR530 <- OLISSpectraMeta %>%
  filter(WL==530) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz521)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz521)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR620 <- OLISSpectraMeta %>%
  filter(WL==620) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz612)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz612)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR660 <- OLISSpectraMeta %>%
  filter(WL==660) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz647)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz647)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR730 <- OLISSpectraMeta %>%
  filter(WL==730) %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz722)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz722)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPURWW <- OLISSpectraMeta %>%
  filter(WL=="WW") %>% 
  mutate(PURNorm = (AbsNorm440*EmNormJaz600)) %>% 
  group_by(WL, Strain, Par_ue, Photoperiod, E_days, O2) %>%
  mutate(PURNormSum = sum(PURNorm)) %>% 
  mutate(SumEmNormJaz = sum(EmNormJaz600)) %>% 
  mutate(PUR = Par_ue*(PURNormSum/SumEmNormJaz)) %>% 
  ungroup() 

OLISSpectraMetaPUR<-rbind(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)

rm(OLISSpectraMetaPUR405, OLISSpectraMetaPUR450, OLISSpectraMetaPUR470, OLISSpectraMetaPUR530, OLISSpectraMetaPUR620, OLISSpectraMetaPUR660, OLISSpectraMetaPUR730, OLISSpectraMetaPURWW)
```

# Filter unrevelant data

```{r filter unrevelant data}
OLISSpectraMetaPUR<-OLISSpectraMetaPUR %>% 
  filter(PUR>=0) 
```

# Calculate daily PUR photon dose

```{r calculate PUR Photon dose}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
  mutate(PURPhotonDose_day =(PUR/2)*Photoperiod*3600)

```


```{r Changes strain names}
OLISSpectraMetaPUR <- OLISSpectraMetaPUR %>%
      mutate(Strain=case_when(Strain=="BA127R"~"PE-rich",
         Strain=="BA77G"~"PC-rich")) 
```



# Create plot

```{r Create plot}

OLISSpectraMetaPUR %>%
  filter(E_days == 7 | E_days == 6) %>% 
  ggplot() +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +
  scale_color_manual(values = c("PC-rich" ="palegreen3", "PE-rich" ="brown4")) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 

```



-------------------------------# Create df with phases of growth---------------------------------

```{r}
MultiCultiDataAll70ExpResup<-OLISSpectraMetaPUR %>% 
  filter(E_days >= 14)  
MultiCultiDataAll70ExpResup$Phase<-"ExpResuply"

All70PCExp1<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days < 14)  
All70PCExp1$Phase<-"Exp"

All70PCExp2<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 8)  
All70PCExp2$Phase<-"Exp"

All70PCExp3<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp3$Phase<-"Exp"

All70PCExp4<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days <= 7)  
All70PCExp4$Phase<-"Exp"

All70PCSt1<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 9 & E_days <=13)  
All70PCSt1$Phase<-"St"

All70PCSt2<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt2$Phase<-"St"

All70PCSt3<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PC-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PCSt3$Phase<-"St"




All70PEExp1<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp1$Phase<-"Exp"

All70PEExp2<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp2$Phase<-"Exp"

All70PEExp3<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days < 14)  
All70PEExp3$Phase<-"Exp"

All70PEExp4<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days <= 7)  
All70PEExp4$Phase<-"Exp"


All70PESt1<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 60) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt1$Phase<-"St"

All70PESt2<-OLISSpectraMetaPUR %>% 
  filter(WL == 530) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt2$Phase<-"St"

All70PESt3<-OLISSpectraMetaPUR %>% 
  filter(WL == 660) %>% 
  filter(Par_ue == 300) %>% 
  filter(Strain == "PE-rich") %>% 
  filter(E_days >= 8 & E_days <=13)  
All70PESt3$Phase<-"St"


OLISSpectraMetaPhase<-rbind(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)

rm(MultiCultiDataAll70ExpResup, All70PCExp1, All70PCExp2, All70PCExp3, All70PCExp4, All70PCSt1, All70PCSt2, All70PCSt3, All70PEExp1, All70PEExp2, All70PEExp3, All70PEExp4, All70PESt1, All70PESt2, All70PESt3)
```



```{r}

OLISSpectraMetaPhase %>%
  ggplot() +
  geom_point(aes(x = WL, y = PUR, colour = as.factor(Strain), shape = as.factor(Run)), show.legend = T) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 


```



# Mean from the absorbance and pur

```{r}
#colnames(OLISSpectraMetaPUR)

OLISSpectraMetaPhasemean<-OLISSpectraMetaPhase %>% 
  # filter(Run!=59) %>% 
  group_by(Strain, Par_ue, WL, O2, nm, Phase) %>%
  
  summarize(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL,  PARPhotonDose_day, PURPhotonDose_day, ObsDate, Absorbance, nm, E_days, AbsNorm440, EmNormJaz722, EmNormJaz600, EmNormJaz647, EmNormJaz612, EmNormJaz521, EmNormJaz469, EmNormJaz441, EmNormJaz393, PUR, PURNorm, Phase,
            
            meanAbsorbance = mean(Absorbance),
            sdAbsorbance = sd(Absorbance),
            meanAbsNorm440 = mean(AbsNorm440),
            sdAbsNorm440 = sd(AbsNorm440),
            meanPURNorm = mean(PURNorm),
            sdPURNorm = sd(PURNorm),
            meanPUR= mean(PUR),
            sdPUR = sd(PUR)) %>%
  ungroup() 
  
OLISSpectraMetaPhasemean<-OLISSpectraMetaPhasemean %>%
  mutate(PURPAR = PUR/Par_ue)
```



```{r Create plot}

OLISSpectraMetaPhase %>%
  filter(Phase == "ExpResuply") %>% 
  ggplot() +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +
  scale_color_manual(values = c("PC-rich" ="palegreen3", "PE-rich" ="brown4")) +
  stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
  scale_fill_identity() +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c (-0.01, 1.6)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 

OLISSpectraMetaPhase %>%
  #filter(E_days == 7 | E_days == 8 | E_days == 6) %>% 
  ggplot() +
  # geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_line(aes(x = nm, y = AbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +
  #scale_color_manual(values = c("PC-rich" ="palegreen3", "PE-rich" ="brown4")) +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 

OLISSpectraMetaPhasemean %>%
  #filter(E_days == 7 | E_days == 8 | E_days == 6) %>% 
  ggplot() +
  # geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +
  geom_line(aes(x = nm, y = meanAbsNorm440, colour = as.factor(Strain)), show.legend = T, size = 0.4) +
  #scale_color_manual(values = c("PC-rich" ="palegreen3", "PE-rich" ="brown4")) +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 

OLISSpectraMetaPhasemean %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanPUR, colour = as.factor(Strain)), show.legend = T) +
  geom_errorbar(aes(x = WL, ymin = meanPUR - sdPUR, ymax = meanPUR + sdPUR, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  #labs(y = "Normalized absorbance", x = "Wavelength (nm)") +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() 
```


```{r Create plot}
lab1=c(expression("PC-rich"), expression("PE-rich"))


#data_textA <- data.frame(Strain  = c("PE-rich"), WL  = c("405"), label = c('italic(a)'))

Spectra<-OLISSpectraMetaPhasemean %>%
  #filter(E_days == 7 | E_days == 8) %>% 
  # filter(E_days == 4 | E_days == 7 | E_days == 6) %>% 
  ggplot() +
  # geom_area(aes(x = nm, y = EmNormJaz722, fill = "gray84"), alpha = 0.6, show.legend = F) +

  geom_area(aes(x = nm, y = meanPURNorm), alpha = 0.2, show.legend = F) +
  #geom_area(aes(x = nm, y = meanPURNorm, fill = "brown4"), alpha = 0.2, show.legend = F, OLISSpectraMetaPUR127) +
  #geom_area(aes(x = nm, y = PURNorm, fill = "brown4"), alpha = 0.2, show.legend = F, OLISSpectraMetaPUR127405) +

  geom_line(aes(x = nm, y = meanPURNorm, colour=as.factor(Strain)), size = 0.5, show.legend = F) +
  #geom_line(aes(x = nm, y = meanPURNorm), colour = "brown4", size = 0.5, show.legend = F, OLISSpectraMetaPUR127) +
  #geom_text(data=data_textA, aes(x=720, y=1.0, label=label), size=6, parse = TRUE) +
  geom_line(aes(x = nm, y = meanAbsNorm440, colour = as.factor(Strain)), show.legend = F, size = 0.4) +
  #geom_line(aes(x = nm, y = AbsNorm440, linetype = as.factor(O2)), show.legend = F, size = 0.4, OLISSpectraMetaPUR127405) +
  scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
  scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
  scale_fill_identity() +
  labs(y = "Normalized absorbance and PUR", x = "Wavelength (nm)") +
  scale_y_continuous(breaks=seq(0, 1.0, by = 1)) +
  scale_x_continuous(breaks=seq(400, 710, by = 100)) +
  coord_cartesian(ylim = c (-0.01, 1.6)) +
  ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = c(0.08,0.90),
        legend.text = element_text(size=10))
Spectra
```

# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_OlisSpectraRaw",".png",sep = "")), height=8, width= 6,  dpi = 300, limitsize = TRUE)
```



---------------------------------------------------------------------------------------------------------



# Create tidy df without all nm

```{r clean df, create smaller df - without absorbance and all nm}
colnames(OLISSpectraMetaPhasemean)

OLISAllPURTidy<-OLISSpectraMetaPhasemean %>% 
  select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, PARPhotonDose_day, PURPhotonDose_day, PUR, meanPUR, sdPUR, E_days, PURPAR, Phase)) %>% 
  unique() %>% 
  mutate(meanPURPARRatio = meanPUR/Par_ue) %>%
  mutate(sdPURPARRatio = sdPUR/Par_ue)
  
OLISAllPURTidy <- OLISAllPURTidy %>% 
  filter(meanPURPARRatio<=1) %>% 
  filter(meanPURPARRatio>0)
```

# Preparing df for creating plot

```{r create tidy PAR photon dose and facets for plot}
  # OLISAllPURTidy <- OLISAllPURTidy %>% 
  # mutate(Oxygen=case_when(O2==21~"250~µM",
  #        O2==0~"2.5~µM"))
```


# Create preliminary plot

```{r Create final PUR/PAR ratio plot}
lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))


OLISAllPURTidy %>%
  ggplot() +
  geom_point(aes(x = E_days, y = meanPURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (d)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
    ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  # ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()


OLISAllPURTidy %>%
  ggplot() +
  geom_point(aes(x = E_days, y = PURPAR, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (d)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
    ggh4x::facet_nested(rows = vars(Strain), cols = vars(WL, Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  # ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()

OLISAllPURTidy %>%
  ggplot() +
  geom_point(aes(x = WL, y = meanPURPARRatio, colour = as.factor(Strain)), alpha = 0.9, size = 3, show.legend = F) +
    geom_errorbar(aes(x = WL, ymin = meanPURPARRatio - sdPURPARRatio, ymax = meanPURPARRatio + sdPURPARRatio, colour = as.factor(Strain)), width=0, size=0.3, show.legend = F) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  #labs(y = "PUR/PAR ratio", x = "Elapsed time (d)") +
  scale_y_continuous(breaks=seq(0, 1.2, by = 0.4)) +
  coord_cartesian(ylim = c(0, 1.5)) +
    ggh4x::facet_nested(rows = vars(Strain), cols = vars(Par_ue, Phase),labeller = labeller(Ex_WL = label_value, WL = label_value)) +
  # ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
  theme_bw()
```
# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_PURPARRatio",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```




------------------------------------------------------------------------------------

# Save Rds for further analysis

```{r save Rds}
saveRDS(OLISSpectraMetaPhasemean, file.path(DataOut, paste(Project, "Processed_OlisSpectraAll.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(OLISAllPURTidy, file.path(DataOut, paste(Project, "Processed_OlisSpectraTidy.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISSpectraMetaPhasemean)
```

# Variable names used in Data Dictionary

```{r}
colnames(OLISAllPURTidy)
```

